Towards planning of infantile cardiac surgery based on simulation

### 2012-02-28 Doc/Miccai/shell-model.tex
adding wireframe images
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@346 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
modifs in section 2
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@347 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

From our point of view, there are several requirements that the model
should be able to fulfill. Namely:

\begin{itemize}
  \item good support for deformations by bending and twisting
  \item the results of the deformation should be global
  \item method should allow arbitrary models and not rely on specific
  structure of the object (e.g. on tubular structure like \cite{Li2009})
  \item the model has to be able to deal with collisions (e.g. between the
  aortic arch and pulmonary artery)
\end{itemize}

@@

\begin{figure}[tbh]
  \centering
  \begin{tabular}{cccc}
    \includegraphics[width=0.24\columnwidth]{img/twist-06-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-08-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-16-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-31-cg.png}
  \end{tabular}
  \caption{Convergence on a twisted cylinder with 6, 8, 16 and 31 nodes
  around the circumference (120, 208, 832 and 3038 elements).
  \christian{Could we add wire-frame images to show the density of the meshes} } 
  \label{fig-convergence}
\end{figure}

>>>>

Infantile cardiac surgery offers a reconfiguration of the blood vessel walls that limits or rectifies the congenital anomalies of the anatomy.
During the surgery, the vessel walls are deformed, cut, and reconnected to other vessels.
To do a planning of the surgery, the geometry changes of these vessel walls (the motions and deformations, their configuration when they are cut or stitched)  must be anticipated.

These requirements ask for a physics-based model for the vessel walls. This model should provide (I) a good support for the deformations by bending and twisting. (II) an accurate modeling of the wall motion when the vessel is cut along its axis (III) global deformations of stitched vessels that capture their final configuration, after surgery (IV) collision response when detected (e.g. between the aortic arch and pulmonary artery).

@@

\begin{figure}[tbh]
  \centering
  \begin{tabular}{cccc}
    \includegraphics[width=0.24\columnwidth]{img/twist-06-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-08-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-16-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-31-cg.png}
    \\
    \includegraphics[width=0.24\columnwidth]{img/twist-06w-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-08w-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-16w-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-31w-cg.png}
  \end{tabular}
  \caption{Convergence on a twisted cylinder with 6, 8, 16 and 31 nodes
  around the circumference (120, 208, 832 and 3038 elements).
  \tomas{improve the wireframe images if there's time} } 
  \label{fig-convergence}
\end{figure}
